---
title: "DanielClark_CaseStudy2_Codebook"
author: "Daniel Clark"
date: "8/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(readxl)
```

## Frito Lay Employee Analysis


This codebook provides an overview of the data as it was received and any modifications that were required to support our analysis. It is a documentation of the variables in the data set, any normalization or modifications that were made, and should support replication of our analysis. 

### Data Files Received

Frito Lay provided our consulting group with thre Comma Delimited files (.csv) file titled Beers.csv & Breweries.csv. 

```{r data import}
employment <- "https://raw.githubusercontent.com/dclark18/MSDS_DanielClark_EmployementAttrition/master/CaseStudy2-data.csv"
traindata <- read.csv(url(employment))

attrition <- 'https://raw.githubusercontent.com/dclark18/MSDS_DanielClark_EmployementAttrition/master/CaseStudy2CompSet%20No%20Attrition.csv'
testattrition <- read.csv(url(attrition))

salary <- 'https://raw.githubusercontent.com/dclark18/MSDS_DanielClark_EmployementAttrition/master/CaseStudy2CompSet%20No%20Salary.csv'
testsalary <- read.csv(url(salary))
```

### Data Collection

It is unclear how this data was collected. Our consulting group contacted the source, but did not receive a description on the methodology used. Because of this, we will have to extrapolate future implications with the data.  

### Initial Data Structure

The data contained within the provided table has the following variable names and types: 

Derived variables include: 

### traindata.csv

```{r}
kable(t(lapply(traindata,class)))%>%
  kable_styling()%>%
  scroll_box(height = 100, width = 500)
```

### testattrition.csv

```{r}
kable(t(lapply(testattrition,class)))%>%
  kable_styling()%>%
  scroll_box(height = 100, width = 500)
```



### testsalary.csv

```{r}
kable(t(lapply(testsalary,class)))%>%
  kable_styling()%>%
  scroll_box(height = 100, width = 500)
```

### Data Cleaning

To more easily analyze Age Groups and Commute Distance, we converted those continuous variables to Ordinal. Also removed columns that didn't have multiple levels. 

```{r, count standard hours}
train <- traindata[,!(names(traindata) %in% c("ID", "StandardHours", "EmployeeNumber", "EmployeeCount", "Over18"))] 
```

```{r, age groups}
train$agegroup <- with(train, ifelse(Age < 25, "18-24", ifelse(Age < 34, "25-34", ifelse(Age < 44, "35-44", ifelse(Age < 52, "45 - 52", "Over53")))))

testattrition$agegroup <- with(testattrition, ifelse(Age < 25, "18-24", ifelse(Age < 34, "25-34", ifelse(Age < 44, "35-44", ifelse(Age < 52, "45 - 52", "Over53")))))

testsalary$agegroup <- with(testsalary, ifelse(Age < 25, "18-24", ifelse(Age < 34, "25-34", ifelse(Age < 44, "35-44", ifelse(Age < 52, "45 - 52", "Over53")))))
```

```{r, distance from home}
# distance grouping
train$DistanceGrouping <- with(train, ifelse(DistanceFromHome > 25, "25+ Miles", ifelse(DistanceFromHome > 18, "19 - 25 Miles", ifelse(DistanceFromHome > 10, "11 - 18 Miles", ifelse(DistanceFromHome >5, "6 - 10 Miles", "Less than 6  Miles")))))

testattrition$DistanceGrouping <- with(testattrition, ifelse(DistanceFromHome > 25, "25+ Miles", ifelse(DistanceFromHome > 18, "19 - 25 Miles", ifelse(DistanceFromHome > 10, "11 - 18 Miles", ifelse(DistanceFromHome >5, "6 - 10 Miles", "Less than 6  Miles")))))

testsalary$DistanceGrouping <- with(testsalary, ifelse(DistanceFromHome > 25, "25+ Miles", ifelse(DistanceFromHome > 18, "19 - 25 Miles", ifelse(DistanceFromHome > 10, "11 - 18 Miles", ifelse(DistanceFromHome >5, "6 - 10 Miles", "Less than 6  Miles")))))

```
